Papers

### 2024-11-19 papers.qmd
add Stony Brook talk

## 2024
N. Winovich, Nick, L. Moynihan, O. Abdelrahman, R. West, S. Dauphin, **J. D. Tucker**, G. Huerta, K. Potter, R. Forrest, C. Phillips, and M. Ebeida, "VoroClust: Scalable Clustering for Remote Sensing", *IEEE Transactions on Geoscience and Remote Sensing*, submitted, 2024.

J.E. Borgert, J. Hannig$, **J.D. Tucker**, L. Arbeeva, A. N. Buck, Y. M. Golightly, S. P. Messier, A. E. Nelson, and J.S. Marron, "Elastic Shape Analysis of Movement Data", *JASA Case Studies and Applications*, submitted, 2024.

A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. 10.3389/fnuen.2024.1331349, 2024. [PDF](Papers/SUR24FNE.pdf)

D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, in revision, 2024. [arxiv preprint](https://arxiv.org/abs/2308.05915)

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *SIAM/ASA Journal on Uncertainty Quantification*, in revision, 2024. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

## Invited Talks
"Bayesian Model Calibration: An Elastic Approach" *Purdue Statistical Colloquium*, February 23, 2024, [Slides](https://jdtuck.github.io/presentations/Purdue_Feb24/Purdue_Feb24.html)

@@

"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019 [Slides](https://jdtuck.github.io/presentations/FDA_Overview/FDA_Overview.html)

>>>>

## 2024
A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. submitted, 2023.

D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

## Invited Talks
"Elastic Functional Data Analsyis: with Applications to Functional Changepoint" *Stony Brook SIAM Speaker*, November 19, 2024, [Slides](https://jdtuck.github.io/presentations/StoneyBrook_Nov_24/StoneyBrook_Nov_24.html)

"Bayesian Model Calibration: An Elastic Approach" *Purdue Statistical Colloquium*, February 23, 2024, [Slides](https://jdtuck.github.io/presentations/Purdue_Feb24/Purdue_Feb24.html)

@@

"Elastic Functional Data Analysis", *Brigham Young University Statistics Colloquium*, December 4, 2019
